---
title: "Find Diverse Podcasts"
author: "Benfeard"
date: "10/29/2020"
output: md_document
---

## Goals

I want to find new podcasts from diverse backgrounds by mining tweets. There is a hashtag, #podsincolor, that can help me find tweets from podcasts whose hosts are People of Color. I want to compile the information into a dataframe and save that as a CSV file for future analyses.

## Load libraries

```{r}
# load twitter library
library(rtweet)
# text mining library
library(tidytext)
# dataframe management and potential plots
library(tidyverse)
```

## Access Token/Secret Method

I need to create a token using my Twitter developer account so I can access the Twitter API. I will put everything in a function, create_token().

NOTE: I don't want to publish my personal keys and token so the github version of this code doesn't contain real keys and tokens.

```{r}
api_key <- "[insert personal key here]"
api_secret_key <- "[insert personal key here]"
access_token <- "[insert personal key here]"
access_token_secret <- "[insert personal key here]"


## authenticate via web browser
token <- create_token(
  app = "OmegaEXE",
  consumer_key = api_key,
  consumer_secret = api_secret_key,
  access_token = access_token,
  access_secret = access_token_secret)
```

# Search for Tweets with the appropriate hashtag

```{r}
podsincolor_tweets <- search_tweets(q = "#podsincolor", n = 10000,
                                      lang = "en",
                                      include_rts = FALSE)

#look at the results
head(podsincolor_tweets$text)
```

## Data Clean-Up


```{r}
#write_csv(podsincolor_tweets, "podsincolor_tweets.csv") -> Error: Flat files can't store the list column 'hashtags'

dput(tweets, "podsincolor_tweets_02Nov2020.txt")
saveRDS(tweets, "podsincolor_tweets_02Nov2020.rds")

each_podcast <- unique(tweets$screen_name)
length(each_podcast)
head(each_podcast)
```

## Word Cloud

```{r}
library(wordcloud)
library(tm)

all_hashtags <- c()

for(entry in tweets$hashtags) {
  for(element in entry){
    all_hashtags <- c(all_hashtags, element)
  }
}

head(all_hashtags)
length(all_hashtags)

wordcloud(all_hashtags, scale = c(2, 1), min.freq = 5, colors = rainbow(30))
```

